---
title: "Experimental Vibratory Analysis"
description: |
  Data analysis for the Article 2
author:
  - first_name: "Fangkai"
    last_name: "Xue"
    url: 
    affiliation: ERPI
    affiliation_url: 
  - first_name: "Fabio"
    last_name: "CRUZ"
    url: 
    affiliation: ERPI
    affiliation_url: 
site: distill::distill_website
# output:
#   distill::distill_article:
#     toc: true
#     toc_depth: 2
#repository_url: https://github.com/LF2L/everest-bio
#bibliography: 03-comportement.bib
#nocite: '@*'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# Options for Knirt
knitr::opts_chunk$set(echo = TRUE,  include=FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '-')

# Packages for the analysis
library(tidyverse)
library(here)
library(readxl)
library(kableExtra)
library(ggpubr)

## Ggplot Theme setting
theme_set(theme_bw(base_size = 15, base_family = "Palatino")) 
```

# Experimental context

> The main idea is to evaluate the influence of printing parameters in the Vibrational response of printed samples

## Data from December 2020
Last update: `r Sys.Date()`

```{r, include=TRUE, echo = FALSE}

# Reading the Data
Anova <- read_excel(here("Data Decembre 2020/ANOVA.xlsx")) 
Anova <- Anova %>% set_names(c("Raster", "Temperature", "Layer", "Speed", "Frequency.I", "Frequency.II" ))

# Changing the variables as factors
Anova <- Anova %>% mutate(Raster = factor(Raster),
                          Temperature = factor(Temperature),
                          Layer = factor(Layer),
                          Speed = factor(Speed)
                          )

# Longer table
Anova <- Anova %>% pivot_longer(cols = Frequency.I:Frequency.II)
Anova <- Anova %>% select(-name)

# Ploting the data
Anova %>%  
  kbl(booktabs = T, digits = c(0, 1, 3, 3, 3, 5),
      caption = "Data for Anova",  
      linesep = "")  %>%
  kable_styling(latex_options = c("striped"))

write_excel_csv2(Anova, "download/Anova.csv")

```

1. [**Vous pouvez telechager ce tableau ici dan ce lien**](download/Anova.csv).

## ANOVA

### Anova without Interactions
```{r Anova.noInter, include=TRUE}
## Creating the Linear Model without interactions
### Witouth interactions
Model.anv <- lm(value ~ Raster+Temperature+Layer+Speed, data = Anova)
anova(Model.anv)
```



### Anova with Interactions

```{r Anova.Inter, include=TRUE}
### With interactions
Model.anv <- lm(value ~ (.)^2  , data = Anova)

#summary(Total_model)
anova(Model.anv)
```


## Graphic of the means

```{r, include=TRUE}
test <- Anova %>% pivot_longer(!value, names_to = "Variables", values_to = "Level") %>% 
  select(Variables, Level, value)

ggboxplot(test, x = "Variables", y = "value", color = "Level",  
          add = "jitter", legend = "top") +
  geom_hline(yintercept = mean(test$value), linetype = 2) +
  coord_cartesian(ylim = c(18, 28))

```

### Interaction Raster Vs. Layer
```{r, include=TRUE}
ggline(Anova, x = "Layer", y = "value", color = "Raster",
       add = c("mean_se"), palette = "jco")
```

### Interaction Temperature Vs. Layer
```{r, include=TRUE}
ggline(Anova, x = "Temperature", y = "value", color = "Layer",
       add = c("mean_se"), palette = "jco")
```
